---
title: "H1-Sample 1"
author: "Beyza Bani"
date: "06-08-2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# Load necessary libraries ------------------------------------------------
library(ggplot2)
library(readxl)
library(dplyr)
library(tidyr)
library(scales)
library(gridExtra) 
library(knitr)
library(kableExtra)
library(broom)
library(knitr)
library(stargazer)
library(rio)
library(lmtest)
library(sandwich)

# Read the data -----------------------------------------------------------
df <- read_excel("C:/Users/User/Desktop/osterloh/schilling/data.xlsx")
```
## H1: Poaching 
Hypothesis: Companies poach women working in leadership positions at other firms to comply with the share of 20 percent female executives. This leads to a reduced tenure of women compared to men.  

Rationale: This practice increases fluctuation among executive females, which translates to shorter tenures compared to their male colleagues.  

Connection to Sampling: To test this hypothesis, we need to know the tenure of men and women, the executive’s prior position and their subsequent position in the respective companies ( sampling of women and first sampling of 72 men).  

Variables needed to test H1  
o Tenure of men and women in the respective companies  
o Prior and subsequent companies in which men and women are employed.  
o Prior and subsequent positions of men and women  

```{r echo=FALSE}
# cleaning ----------------------------------------------------------------

df <- df[-1, ]%>% 
  select(Austrittsjahr, Jahrgang, Gender, Sample, Stellenantritt, Nationality, Nationality_co, Branche, PriorPosition,	PriorWechselUnternehmen,	prior_code, tenure_prior, prior_position_code, prior_status, schilling_status, highest_degree, ausbildungsort, field_of_study) %>%
  mutate_all(as.character) %>%
  mutate_all(~ recode(., "NA" = NA_character_, "N/A" = NA_character_))


# New variables -----------------------------------------------------------
df_age <- df %>%
  drop_na(Jahrgang, Stellenantritt) %>%
  mutate(age_start = as.numeric(Stellenantritt) - as.numeric(Jahrgang))%>% 
  mutate(age_exit = as.numeric(Austrittsjahr) - as.numeric(Jahrgang)) %>% 
  mutate(current_age = 2023 - as.numeric(Jahrgang))
df_tenure <- df %>% 
  drop_na(Stellenantritt) %>% 
  mutate(tenure = as.numeric(Austrittsjahr) - as.numeric(Stellenantritt))

#table(df$prior_code)
#table(df$prior_status)
#table(df$highest_degree)
#table(df$ausbildungsort)
#table(df$field_of_study)
#sum(is.na(df$highest_degree))
```

## Sample 1


```{r echo=FALSE}
dfs1 <- df_tenure %>%
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code) %>%
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>% 
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male"))) %>% 
mutate(tenure_group = case_when(
    tenure >= 1 & tenure <= 3 ~ "1-3 years",
    tenure >= 4 & tenure <= 6 ~ "4-6 years",
    tenure >= 7 & tenure <= 9 ~ "7-9 years",
    tenure >= 10 & tenure <= 12 ~ "10-12 years",
    tenure >= 13 & tenure <= 27 ~ "13+ years",))

# Calculate percentage distribution
dfs1_percentage <- dfs1 %>%
  group_by(Gender, prior_code_group, tenure_group) %>%
  summarise(count = n()) %>%
  group_by(Gender, prior_code_group) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()

# Plot the data
dfs1_percentage %>% 
  mutate(tenure_group = factor(tenure_group, levels = c(
    "1-3 years", "4-6 years", "7-9 years", "10-12 years", "13+ years"))) %>% 
  ggplot(aes(x = factor(prior_code_group), y = percentage, fill = tenure_group)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~ Gender) +
  labs(x = "Prior Wechsel Unternehmen", y = "Percentage", fill = "Tenure Group") +
  ggtitle("Percentage Distribution of Tenure Group by Prior Wechsel Unternehmen and Gender (Sample1") +
  theme_minimal() +
  geom_text(aes(label = sprintf("%.1f%% (%d)", percentage, count)), 
            position = position_stack(vjust = 0.5), size = 3)

```


```{r echo=FALSE}

#Previous company and Gender

df_previous <- df %>%
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code) %>% 
   mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>% 
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))

# Calculate percentages
df_percentage <- df_previous %>%
  group_by(prior_code_group, Gender) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

# Create the percentage bar plot with custom labels and percentages on the bars
ggplot(df_percentage, aes(x = factor(prior_code_group), y = percentage, fill = Gender, label = paste0(round(percentage, 1), "% (", count, ")"))) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(position = position_dodge(width = 0.9), vjust = -0.5, size = 3) +
  scale_fill_manual(values = c("Female" = "#FF6347", "Male" = "#4682B4")) + # Custom colors for Female and Male
  labs(title = "Percentage of Gender by Prior Company Change", x = "Prior Company Change", y = "Percentage", fill = "Gender") +
  theme_minimal()


```





```{r echo=FALSE}
#stayed in the same company

df_stayed <- df %>%
  filter(Sample == 0 | Sample == 1) %>%  
  drop_na(prior_code) %>%
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>% 
  filter(prior_code_group == "stayed in the same company") %>% 
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))

#table(df_stayed$Nationality_co)
#table(df_stayed$Branche)
#table(df_stayed$tenure_prior)
#table(df_stayed$prior_position_code)


# plotting Nationality_co by Gender with descriptive labels
df_stayed_nationality <- df_stayed %>% 
  drop_na(Nationality_co) %>% 
  mutate(Nationality_co = factor(Nationality_co, 
                                 levels = c(0, 1),
                                 labels = c("Schweiz", "Foreign")))

ggplot(df_stayed_nationality, aes(x = Nationality_co, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Nationality Distribution by Gender (Stayed in the Same Company)",
       x = "Nationality",
       y = "Count") +
  theme_minimal()


# Plot for Branche by Gender
df_stayed_branche <- df_stayed %>% 
  drop_na(Branche)
ggplot(df_stayed_branche, aes(x = factor(Branche), fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Industry Distribution by Gender (Stayed in the Same Company)",
       x = "Industry (Branche)",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# tenure prior + gender --> same company
 df_stayed_tenure <- df_stayed %>%
  mutate(tenure_prior = as.numeric(tenure_prior)) %>%  
  mutate(tenure_prior = ifelse(tenure_prior == "", NA, tenure_prior)) %>%  
  drop_na(tenure_prior) %>%
  mutate(tenure_prior_group = factor(case_when(
    tenure_prior >= 0 & tenure_prior <= 2 ~ "0-2 years",
    tenure_prior >= 3 & tenure_prior <= 5 ~ "3-5 years",
    tenure_prior >= 6 & tenure_prior <= 10 ~ "6-10 years",
    tenure_prior >= 11 & tenure_prior <= 30 ~ "11+ years"),
    levels = c("0-2 years", "3-5 years", "6-10 years", "11+ years")  
  ))

# Plot with custom colors and correct ordering
ggplot(df_stayed_tenure, aes(x = tenure_prior_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Tenure Prior Group Distribution by Gender (Stayed in the Same Company)",
       x = "Tenure Prior Group",
       y = "Count") +
  theme_minimal()

# Include Nationality Layer in Tenure Data
df_stayed_tenure <- df_stayed %>%
  mutate(tenure_prior = as.numeric(tenure_prior)) %>%  # Ensure tenure_prior is numeric
  mutate(tenure_prior = ifelse(tenure_prior == "", NA, tenure_prior)) %>%  # Convert empty strings to NA
  drop_na(tenure_prior) %>%
  mutate(tenure_prior_group = factor(case_when(
    tenure_prior >= 0 & tenure_prior <= 2 ~ "0-2 years",
    tenure_prior >= 3 & tenure_prior <= 5 ~ "3-5 years",
    tenure_prior >= 6 & tenure_prior <= 10 ~ "6-10 years",
    tenure_prior >= 11 & tenure_prior <= 30 ~ "11+ years"),
    levels = c("0-2 years", "3-5 years", "6-10 years", "11+ years")  # Specify the correct order of levels
  )) %>%
  drop_na(Nationality_co) %>% 
  mutate(Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))  # Add Nationality as a factor

# Plot with custom colors, correct ordering, and nationality layer
ggplot(df_stayed_tenure, aes(x = tenure_prior_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  facet_wrap(~ Nationality_co) +  # Add facetting by nationality
  labs(title = "Tenure Prior Group Distribution by Gender and Nationality (Stayed in the Same Company)",
       x = "Tenure Prior Group",
       y = "Count",
       fill = "Gender") +
  theme_minimal()


# Plotting prior_position_code by Gender with descriptive labels
df_stayed_position <- df_stayed %>% 
  drop_na(prior_position_code) %>% 
  mutate(prior_position_code = factor(prior_position_code, 
                                      levels = c(0, 1, 2, 3),
                                      labels = c("GL to GL", "GL to VR", 
                                                 "More Responsibility", 
                                                 "Less Responsibility")))

ggplot(df_stayed_position, aes(x = prior_position_code, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Prior Position Code Distribution by Gender (Stayed in the Same Company)",
       x = "Prior Position Code",
       y = "Count") +
  theme_minimal()


# Updated code for plotting prior_position_code by Gender with Nationality layer
df_stayed_position <- df_stayed %>% 
  drop_na(prior_position_code) %>% 
  mutate(prior_position_code = factor(prior_position_code, 
                                      levels = c(0, 1, 2, 3),
                                      labels = c("GL to GL", "GL to VR", 
                                                 "More  \nResponsibility", 
                                                 "Less  \nResponsibility"))) %>%
  drop_na(Nationality_co) %>% 
  mutate(Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))  # Add Nationality as a factor

ggplot(df_stayed_position, aes(x = prior_position_code, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  facet_wrap(~ Nationality_co) +  # Add facetting by nationality
  labs(title = "Prior Position Code Distribution by Gender and Nationality (Stayed in the Same Company)",
       x = "Prior Position Code",
       y = "Count") +
  theme_minimal()


# Tenure and Gender
df_stayed_tenure_now <- df_tenure %>% 
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code, Gender, tenure) %>%  
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>%
  filter(prior_code_group == "stayed in the same company") %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male"))) %>% 
  mutate(tenure_group = factor(case_when(
    tenure >= 1 & tenure <= 3 ~ "1-3 years",
    tenure >= 4 & tenure <= 6 ~ "4-6 years",
    tenure >= 7 & tenure <= 9 ~ "7-9 years",
    tenure >= 10 & tenure <= 12 ~ "10-12 years",
    tenure >= 13 & tenure <= 27 ~ "13+ years"),
    levels = c("1-3 years", "4-6 years", "7-9 years", "10-12 years", "13+ years")))  

# Plot with custom colors and correct ordering
ggplot(df_stayed_tenure_now, aes(x = tenure_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Tenure by Gender (Stayed Company)",
       x = "Tenure",
       y = "Count") +
  theme_minimal()


# Tenure and Gender with Nationality layer
df_stayed_tenure_now <- df_tenure %>% 
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code, Gender, tenure) %>%  
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>%
  filter(prior_code_group == "stayed in the same company") %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male"))) %>% 
  mutate(tenure_group = factor(case_when(
    tenure >= 1 & tenure <= 3 ~ "1-3 years",
    tenure >= 4 & tenure <= 6 ~ "4-6 years",
    tenure >= 7 & tenure <= 9 ~ "7-9 years",
    tenure >= 10 & tenure <= 12 ~ "10-12 years",
    tenure >= 13 & tenure <= 27 ~ "13+ years"),
    levels = c("1-3 years", "4-6 years", "7-9 years", "10-12 years", "13+ years"))) %>%
  drop_na(Nationality_co) %>% 
  mutate(Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))  # Add Nationality as a factor

# Plot with custom colors, correct ordering, and nationality layer
ggplot(df_stayed_tenure_now, aes(x = tenure_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  facet_wrap(~ Nationality_co) +  # Add facetting by nationality
  labs(title = "Tenure by Gender and Nationality (Stayed Company)",
       x = "Tenure Group",
       y = "Count",
       fill = "Gender") +
  theme_minimal()


```



```{r echo=FALSE}
#changed the company

# Filter for individuals who changed companies
df_changed <- df %>%
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code) %>%
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>%
  filter(prior_code_group == "changed company") %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))

#table(df_women_changed$Nationality_co)
#table(df_women_changed$Branche)
#table(df_women_changed$tenure_prior)
#table(df_women_changed$prior_position_code)


# Plot for Nationality_co by Gender with descriptive labels and custom colors
df_changed_nationality <- df_changed %>% 
  drop_na(Nationality_co) %>% 
  mutate(Nationality_co = factor(Nationality_co, 
                                 levels = c(0, 1),
                                 labels = c("Schweiz", "Foreign")))

ggplot(df_changed_nationality, aes(x = Nationality_co, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Nationality Distribution by Gender (Changed Company)",
       x = "Nationality",
       y = "Count") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal()


# Plot for Branche by Gender with custom colors
df_changed_branche <- df_changed %>%
  drop_na(Branche)

ggplot(df_changed_branche, aes(x = factor(Branche), fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Industry Distribution by Gender (Changed Company)",
       x = "Industry (Branche)",
       y = "Count") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Ensure proper NA handling and ordering of tenure_prior_group
df_changed_tenure <- df_changed %>%
  mutate(tenure_prior = as.numeric(tenure_prior)) %>%  # Ensure tenure_prior is numeric
  mutate(tenure_prior = ifelse(tenure_prior == "", NA, tenure_prior)) %>%  # Convert empty strings to NA
  drop_na(tenure_prior) %>%
  mutate(tenure_prior_group = factor(case_when(
    tenure_prior >= 0 & tenure_prior <= 2 ~ "0-2 years",
    tenure_prior >= 3 & tenure_prior <= 5 ~ "3-5 years",
    tenure_prior >= 6 & tenure_prior <= 10 ~ "6-10 years",
    tenure_prior >= 11 & tenure_prior <= 30 ~ "11+ years"),
    levels = c("0-2 years", "3-5 years", "6-10 years", "11+ years")  # Specify the correct order of levels
  ))

# Plot with custom colors and correct ordering
ggplot(df_changed_tenure, aes(x = tenure_prior_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Tenure Prior Group Distribution by Gender (Changed Company)",
       x = "Tenure Prior Group",
       y = "Count") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal()



# Plot for prior_position_code by Gender with custom colors
df_changed_position <- df_changed %>%
  drop_na(prior_position_code) %>%
  mutate(prior_position_code = factor(prior_position_code,
                                      levels = c(0, 1, 2, 3),
                                      labels = c("GL to GL", "GL to VR", 
                                                 "More Responsibility", 
                                                 "Less Responsibility")))

ggplot(df_changed_position, aes(x = prior_position_code, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Prior Position Code Distribution by Gender (Changed Company)",
       x = "Prior Position Code",
       y = "Count") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal()


# Plot for prior_position_code by Gender and Nationality with custom colors
df_changed_position <- df_changed %>%
  drop_na(prior_position_code) %>%
  mutate(prior_position_code = factor(prior_position_code,
                                      levels = c(0, 1, 2, 3),
                                      labels = c("GL to GL", 
                                                 "GL to VR", 
                                                 "More \nResponsibility", 
                                                 "Less \nResponsibility"))) %>%
  mutate(Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))  # Add Nationality as a factor

# Plot with custom colors, correct ordering, and nationality layer
ggplot(df_changed_position, aes(x = prior_position_code, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  facet_wrap(~ Nationality_co) +  # Add facetting by nationality
  labs(title = "Prior PositionDistribution by Gender and Nationality (Changed Company)",
       x = "Prior Position",
       y = "Count") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal()


# Tenure and Gender
df_changed_tenure_now <- df_tenure %>% 
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code, Gender, tenure) %>%  
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>%
  filter(prior_code_group == "changed company") %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male"))) %>% 
  mutate(tenure_group = factor(case_when(
    tenure >= 1 & tenure <= 3 ~ "1-3 years",
    tenure >= 4 & tenure <= 6 ~ "4-6 years",
    tenure >= 7 & tenure <= 9 ~ "7-9 years",
    tenure >= 10 & tenure <= 12 ~ "10-12 years",
    tenure >= 13 & tenure <= 27 ~ "13+ years"),
    levels = c("1-3 years", "4-6 years", "7-9 years", "10-12 years", "13+ years")))  

# Plot with custom colors and correct ordering
ggplot(df_changed_tenure_now, aes(x = tenure_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Tenure by Gender (Changed Company)",
       x = "Tenure",
       y = "Count") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal()

```


```{r echo=FALSE}
#prior position change and gender

df_position <- df %>%
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_position_code) %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")),
         prior_position_code = factor(prior_position_code, 
                                      levels = c(0, 1, 2, 3), 
                                      labels = c(`0` = "Wechsel von \nGL zu GL",
                                                 `1` = "Wechsel von \nGL zu VR",
                                                 `2` = "Wechsel zu Position\n mit mehr \nVerantwortung",
                                                 `3` = "Wechsel zu Position\n mit weniger \nVerantwortung")))

# Create a summary table for counts and percentages
df_summary <- df_position %>%
  group_by(Gender, prior_position_code) %>%
  summarise(Count = n()) %>%
  ungroup() %>%
  group_by(Gender) %>%
  mutate(Percentage = Count / sum(Count) * 100)
# Create the bar plot
ggplot(df_summary, aes(x = prior_position_code, y = Count, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 0), "% (", Count, ")")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.2,
            size = 3) +
  scale_fill_manual(values = c("Female" = "#FF9999", "Male" = "#9999FF")) + # Custom colors
  labs(title = "Prior Position Change by Gender",
       x = "Prior Position Code",
       y = "Count",
       fill = "Gender") +
  theme_minimal() 



# Tenure and Gender with Nationality layer for Changed Company
df_changed_tenure_now <- df_tenure %>% 
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_code, Gender, tenure) %>%  
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>%
  filter(prior_code_group == "changed company") %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male"))) %>% 
  mutate(tenure_group = factor(case_when(
    tenure >= 1 & tenure <= 3 ~ "1-3 years",
    tenure >= 4 & tenure <= 6 ~ "4-6 years",
    tenure >= 7 & tenure <= 9 ~ "7-9 years",
    tenure >= 10 & tenure <= 12 ~ "10-12 years",
    tenure >= 13 & tenure <= 27 ~ "13+ years"),
    levels = c("1-3 years", "4-6 years", "7-9 years", "10-12 years", "13+ years"))) %>%
  mutate(Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))  # Add Nationality as a factor

# Plot with custom colors, correct ordering, and nationality layer
ggplot(df_changed_tenure_now, aes(x = tenure_group, fill = Gender)) +
  geom_bar(position = "dodge") +
  geom_text(stat = "count", aes(label = ..count..), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  facet_wrap(~ Nationality_co) +  # Add facetting by nationality
  labs(title = "Tenure by Gender and Nationality (Changed Company)",
       x = "Tenure Group",
       y = "Count",
       fill = "Gender") +
  scale_fill_manual(values = c("Female" = "darkred", "Male" = "darkblue")) +
  theme_minimal()

```


```{r echo=FALSE}
# Tenure in prior companies and Gender

df_prior_tenure <- df %>%
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(tenure_prior) %>%
  mutate(tenure_prior = as.numeric(tenure_prior)) %>% 
mutate(tenure_prior_group = case_when(
    tenure_prior >= 0 & tenure_prior <= 2 ~ "0-2 years",
    tenure_prior >= 3 & tenure_prior <= 5 ~ "3-5 years",
    tenure_prior >= 6 & tenure_prior <= 10 ~ "6-10 years",
    tenure_prior >=11 & tenure_prior <= 30 ~ "11+ years")) %>%
mutate(tenure_prior_group = factor(tenure_prior_group, 
                                   levels = c("0-2 years", "3-5 years", "6-10 years", "11+ years"))) %>% 
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))

# Create a summary table for counts and percentages
df_summary_tenure <- df_prior_tenure %>%
  group_by(Gender, tenure_prior_group) %>%
  summarise(Count = n()) %>%
  ungroup() %>%
  group_by(Gender) %>%
  mutate(Percentage = Count / sum(Count) * 100)

# Create the bar plot with custom colors
ggplot(df_summary_tenure, aes(x = tenure_prior_group, y = Count, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 0), "% (", Count, ")")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.2,
            size = 3) +
  scale_fill_manual(values = c("Female" = "#E69F00", "Male" = "#56B4E9")) + # Custom colors
  labs(title = "Tenure Prior by Gender",
       x = "Tenure Prior Group",
       y = "Count",
       fill = "Gender") +
  theme_minimal()
```

```{r echo=FALSE}
# Aufstieg und Abstieg

df_status <- df %>% 
    filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_status) %>% 
  mutate(p_status = case_when( 
    prior_status == "nicht vergleichbar (von VR zu GL)" | 
      prior_status == "Nicht Vergleichbar (VR)" ~ "Nicht Vergleichbar",
    TRUE ~ prior_status)) %>% 
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))
  


df_status <- df %>% 
  filter(Sample == 0 | Sample == 1) %>%
  drop_na(prior_status) %>% 
  mutate(p_status = case_when( 
    prior_status == "nicht vergleichbar (von VR zu GL)" | 
      prior_status == "Nicht Vergleichbar (VR)" ~ "Nicht Vergleichbar",
    TRUE ~ prior_status)) %>%
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))

# Count and percentage calculation
df_summary <- df_status %>%
  group_by(Gender, p_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with dodge position and both count and percentage labels
ggplot(df_summary, aes(x = Gender, y = count, fill = p_status)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(count, " (", round(percentage, 1), "%)")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Bar Plot for Gender and Prior Status Change", x = "Gender", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1")



df_status_n <- df %>% 
    filter(Sample == 0 | Sample == 1) %>%
    drop_na(prior_status, Nationality_co) %>%  # Dropping rows with NA in prior_status or Nationality_co
    mutate(p_status = case_when( 
        prior_status == "nicht vergleichbar (von VR zu GL)" | 
        prior_status == "Nicht Vergleichbar (VR)" ~ "Nicht Vergleichbar",
        TRUE ~ prior_status)) %>% 
    mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")),
           Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign"))) 

# Count and percentage calculation with Nationality_co included
df_summary <- df_status_n %>%
  group_by(Gender, Nationality_co, p_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(Gender, Nationality_co) %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with dodge position and both count and percentage labels, with Nationality_co as a facet layer
ggplot(df_summary, aes(x = Gender, y = count, fill = p_status)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(count, " (", round(percentage, 1), "%)")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Bar Plot for Gender, Nationality, and Prior Status Change", x = "Gender", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~ Nationality_co)

```

```{r echo=FALSE}
# Schilling - Aufstieg und Abstieg

#table(df$schilling_status)
#table(df$prior_status)
df_schilling_status <- df %>% 
    filter(Sample == 0 | Sample == 1) %>%
    drop_na(schilling_status) %>% 
    mutate(s_status = case_when( 
        schilling_status == "Nichr Vergleichbar" | 
        schilling_status == "Nicht Aufstieg" | 
        schilling_status == "(Früh)Pension" ~ "Nicht Vergleichbar",
        schilling_status == "Aufsteigend" ~ "Aufstieg",
        TRUE ~ schilling_status)) %>% 
    mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))

  


# Count and percentage calculation
df_summary <- df_schilling_status %>%
  group_by(Gender, s_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with dodge position and both count and percentage labels
ggplot(df_summary, aes(x = Gender, y = count, fill = s_status)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(count, " (", round(percentage, 1), "%)")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Bar Plot for Gender and Schilling Status Change", x = "Gender", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1")



#Naitonality

# Schilling - Aufstieg und Abstieg

df_schilling_status_n <- df %>% 
    filter(Sample == 0 | Sample == 1) %>%
    drop_na(schilling_status, Nationality_co) %>%  
    mutate(s_status = case_when( 
        schilling_status == "Nichr Vergleichbar" | 
        schilling_status == "Nicht Aufstieg" | 
        schilling_status == "(Früh)Pension" ~ "Nicht Vergleichbar",
        schilling_status == "Aufsteigend" ~ "Aufstieg",
        TRUE ~ schilling_status)) %>% 
    mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")),
           Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))


# Count and percentage calculation with Nationality_co included
df_summary <- df_schilling_status_n %>%
  group_by(Gender, Nationality_co, s_status) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(Gender, Nationality_co) %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with dodge position and both count and percentage labels, with Nationality_co as a facet layer
ggplot(df_summary, aes(x = Gender, y = count, fill = s_status)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(count, " (", round(percentage, 1), "%)")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Bar Plot for Gender, Nationality, and Schilling Status Change", x = "Gender", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~ Nationality_co)
  
```


```{r echo=FALSE}
#Highest degree and Gender

df_degree <- df %>% 
   filter(Sample == 0 | Sample == 1) %>%
   drop_na(highest_degree) %>% 
   mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")),
          highest_degree = factor(highest_degree, levels = c(1, 2, 3, 4), 
                                  labels = c("Bachelor's degree", "Master's degree/MBA", "PhD", "Other")))

# Count and percentage calculation
df_summary <- df_degree %>%
  group_by(Gender, highest_degree) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(Gender) %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with dodge position and both count and percentage labels
ggplot(df_summary, aes(x = Gender, y = count, fill = highest_degree)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(count, " (", round(percentage, 1), "%)")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Bar Plot for Gender and Highest Degree", x = "Gender", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1")

  
```

```{r echo=FALSE}
# Filter and mutate data
df_degree <- df %>% 
   filter(Sample == 0 | Sample == 1) %>%
   drop_na(highest_degree, Nationality_co) %>%  # Dropping rows with NA in highest_degree or Nationality_co
   mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")),
          highest_degree = factor(highest_degree, levels = c(1, 2, 3, 4), 
                                  labels = c("Bachelor's degree", "Master's degree/MBA", "PhD", "Other")),
          Nationality_co = factor(Nationality_co, levels = c(0, 1), labels = c("Schweiz", "Foreign")))

# Count and percentage calculation
df_summary <- df_degree %>%
  group_by(Gender, Nationality_co, highest_degree) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(Gender, Nationality_co) %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with dodge position and both count and percentage labels, with Nationality_co as a facet layer
ggplot(df_summary, aes(x = Gender, y = count, fill = highest_degree)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(count, " (", round(percentage, 1), "%)")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Bar Plot for Gender, Nationality, and Highest Degree", x = "Gender", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~ Nationality_co)

```

```{r echo=FALSE}
df_age <- df %>% 
  filter(Sample== 0 | Sample==1) %>%
    drop_na(Jahrgang, Stellenantritt, prior_code) %>%
  mutate(prior_code_group = case_when(
    prior_code == 0 | prior_code == 1 | prior_code == 2 ~ "changed company",
    prior_code == 3 ~ "stayed in the same company")) %>% 
  mutate(age_start = as.numeric(Stellenantritt) - as.numeric(Jahrgang))%>% 
  mutate(age_exit = as.numeric(Austrittsjahr) - as.numeric(Jahrgang)) %>% 
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male"))) %>% 
  mutate(age_start_group = case_when(
    age_start >= 28 & age_start <= 44 ~ "younger than 45",
    age_start >= 45 & age_start <= 54 ~ "45-54 years old",
    age_start >= 55 & age_start <= 73 ~ "55+ years old",)) %>% 
  mutate(age_exit_group = case_when(
    age_exit >= 28 & age_exit <= 44 ~ "younger than 45",
    age_exit >= 45 & age_exit <= 54 ~ "45-54 years old",
    age_exit >= 55 & age_exit <= 73 ~ "55+ years old",))
```


```{r echo=FALSE}
# Status change from previous position and Gender
# Data Preparation
df_anova <- df_tenure %>%
  filter(Sample == 0 | Sample == 1) %>%  # Select Sample 1
  drop_na(tenure, Gender, prior_code) %>%  # Ensure no missing values
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")),
         prior_code_group = factor(ifelse(prior_code == 3, "Stayed", "Changed")))  # Categorize prior_code

# Perform ANOVA
anova_result <- aov(tenure ~ Gender * prior_code_group, data = df_anova)

# Summary of ANOVA
summary(anova_result)





```

```{r echo=FALSE}
# T-Test Analysis
# Testing the difference in tenure between men and women based on prior company change status

# Preparing the data for the t-test
df_ttest <- df_tenure %>%
  filter(Sample == 0 | Sample == 1) %>%  # Select Sample 1
  drop_na(tenure, Gender, prior_code) %>%  # Remove missing values
  mutate(Gender = factor(Gender, levels = c(0, 1), labels = c("Female", "Male")))  # Convert Gender to factor

# Conducting an independent two-sample t-test to compare the mean tenure of males and females
t_test_result <- t.test(tenure ~ Gender, data = df_ttest)

# Displaying the t-test results
t_test_result

# Summarizing the test results
tidy(t_test_result)


```